---
title: "JSONValidate"
author: "Leif Jonsson"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

JSONValidate is an R wrapper around an efficient C++ JSON Schema validator called 'rapidjson'. You can read more about 'rapodjson' here: https://github.com/miloyip/rapidjson. JSON files can be *well-formed* and/or *valid*. A well-formed JSON file conforms to the *syntactic* 
requirements of JSON. Additionaly a *valid* JSON file conforms to a specified JSON Schema. 

JSONValidate via 'rapidjson' supports JSON Schema Draft v4. 2016-09-09: RapidJSON passed 262 out of 263 tests in JSON Schema Test Suite (Json Schema draft 4).

## Usage Scenarios

JSONValidate support four main usage scenarios. 

  * Validate a JSON file against a JSON Schema file
  * Validate a JSON string against a JSON Schema file
  * Validate a JSON file against a JSON Schema string
  * Validate a JSON string against a JSON Schema string

## Validation Results

The result of a validation contains four fields

  * value - A value of 0 on correct applications, non-zero otherwise
  * message - A message containging a string describing the result
  * jsonfile - A path to the input file given
  * schema - A path to the schema file given or a string representation of the schema if given as a string

## Examples

### File - File Example

Example using a schema file on a well-formed and valid JSON file returns a 0 value.

```{r}
library(JSONValidate)
validjson     <- system.file("extdata", "item-3.json", package = "JSONValidate")
schemafile    <- system.file("extdata", "schema.json", package = "JSONValidate")

result <- validate_jsonfile_with_schemafile(validjson, schemafile)
print(result$value)

malformedjson <- system.file("extdata", "malformed-json.json", package = "JSONValidate")

print(result$message)

```

Using validate_* on a syntactically invalid JSON file returns a 1XX error.

```{r}
malformedjson <- system.file("extdata", "malformed-json.json", package = "JSONValidate")

result <- validate_jsonfile_with_schemafile(malformedjson, schemafile)
print(result$value)

print(result$message)
```

In addition to containing the resulting *value* the result also contains the input Schema and JSON file.
```{r}
cat("Schema that the function was called with:")
print(result$schema)

cat("JSON File that the function was called with:")
print(result$jsonfile)
```

Using validate_* on a syntactically correct JSON but invalid (file does not conform to schema) file returns a 2XX error.

```{r}
invalidjson  <- system.file("extdata", "item-2.json", package = "JSONValidate")

result <- validate_jsonfile_with_schemafile(invalidjson, schemafile)

print(result$value)

print(result$message)
```

Using validate_* on missing files throws and error.

```{r}
result = tryCatch({
    validate_jsonfile_with_schemafile("missing", schemafile)
}, error = function(e) {
    print(e)
})

result = tryCatch({
validate_jsonfile_with_schemafile(validjson, "missing")
}, error = function(e) {
    print(e)
})
```

## More Examples

### JSON String - Schema File Example

Using the string API, string JSON, schema file.
```{r}
json_code <- "{\"category\": \"book\", \"price\": 25,  \"title\": \"abrakadabra\"}"
result <- validate_result <- validate_json_with_schemafile(json_code, schemafile)
print(result$value)
print(result$message)
```

### JSON string - Schema string Example

Using the string API, string JSON, string schema.

```{r}
json_code <- "{\"category\": \"book\", \"price\": 25,  \"title\": \"abrakadabra\"}"
schema_code     <- readChar(schemafile, file.info(schemafile)$size)
print(schema_code)
result <- validate_result <- validate_json_with_schema(json_code, schema_code)
print(result$value)
print(result$message)
print(result$schema)
```
